Measuring Individual Partisan Harm in Redistricting

### 2021-09-06 paper/paper.Rmd
fixed metrics; WI sim

The expected harm to an individual $i\in\Voters$ voter then becomes $$
   \E[H\mid I=i] = \Pr\qty(V(i)\neq\win(Q(i), V, Q)
    \text{ and }V(i)=\win(\tilde Q(i), V, \tilde Q)),
$$

@@

In the districting plan examples of Figure \ref{fig:mini-harm}, the fairness of the Democratic gerrymander of Mininois is $-0.494$, the fairness of the Democratic gerrymander of Minissouri is $-0.415$, and the fairness of the Republican gerrymander of Minissouri is $0.450$, where positive values indicate Republican bias.
In other words, the average Republican voter in Mininois is 49.4% more likely to be represented by a Democrat than an average Democrat is to be represented by a Republican, compared to the utility-maximizing plan in Figure \ref{fig:mini-util-opt}(a).

>>>>

The expected harm to an individual $i\in\Voters$ voter then becomes $$
   \E[H\mid I=i] = \Pr[V(i)\neq\win(Q(i), V, Q)
    \text{ and }V(i)=\win(\tilde Q(i), V, \tilde Q)],
$$

@@

In the districting plan examples of Figure \ref{fig:mini-harm}, the fairness of the Democratic gerrymander of Mininois is $-0.519$, the fairness of the Democratic gerrymander of Minissouri is $-0.415$, and the fairness of the Republican gerrymander of Minissouri is $0.450$, where positive values indicate Republican bias.
In other words, the average Republican voter in Mininois is 51.9% more likely to be represented by a Democrat than an average Democrat is to be represented by a Republican, compared to the utility-maximizing plan in Figure \ref{fig:mini-util-opt}(a).
